---
title: "insert title here"
author: "insert name here"
date: "insert date here"
output: html_document
---

This document presents some exploratory analyses of a dataset coded from ... insert a short description here

##Two-Mode Network

```{r}
dat <- read.csv('/path/to/dataset.csv', row.names = 1) # import data and use the values in column 1 as row names
dat[is.na(dat)] <- 0  # binarize the network

## not run
# Make sure that the rows of the matrix contain the first mode and the columns the second mode.
#dat <- t(dat) # transpose the matrix if not
```


Now let's use the [R-package **tnet**](https://cran.r-project.org/web/packages/tnet/tnet.pdf) to treat this matrix as a two-mode network, and **sna** for network plotting and analysis functions. **igraph** must also be installed as it is one of **tnet**'s dependencies. Also load the packages **ggplot2** and **reshape2** for aditional plotting functions and **magrittr** for piping functions to enhance code readability.

If you do not have these packages installed, copy and paste the following code into the R console:
```{r, eval=F}
doInstall <- TRUE  # Change to FALSE if you don't want packages installed.
toInstall <- c("tnet", "ggplot2", "magrittr", "reshape2", "sna", "igraph")
if(doInstall){install.packages(toInstall, repos = "http://cran.r-project.org")}
lapply(toInstall, library, character.only = TRUE)
```

```{r message = F}
library(tnet)
library(sna)
library(magrittr)
library(ggplot2)
library(reshape2)
```
  
Plot the raw two-mode data, with the first mode in red and the second in blue.
  
```{r fig.width=10, fig.height=10}
gplot(dat, gmode = 'twomode', usearrows = F, displayisolates = F, displaylabels = T,label.cex = .5)
```
  
  Let's use **tnet** to create a binary two-mode network.
  
```{r}
mode2 <- as.tnet(dat, type = 'binary two-mode tnet')
```


##One-mode networks
Now we can use **tnet** to *project* the two-mode data into a one-mode format using the **projecting_tm()** function. There are three different projection methods we can use by changing the **method** argument to **projecting_tm()**. The *binary* method simply creates an unweighted one-mode network. The *sum* method weights the ties by the number of co-occurrances. The *Newman* method starts with the number of co-occurrences but downweights ties that pass through more highly-connected second-mode nodes. [Click here for more information on these projection methods](http://toreopsahl.com/tnet/two-mode-networks/projection/).
 
 Let's define a function to create **sna**-compatible adjacency matrices from a **tnet** edgelist, and apply that to projected one-mode networks created using each of the above methods.

```{r}
sna.format <- function(net){
     net <- as.matrix(net)
     N <- max(c(net[,"i"],net[,"j"]))
     g <- matrix(data=0, nrow=N, ncol=N)
     g[net[,c("i","j")]] <- net[,"w"]
     g <- as.sociomatrix.sna(g)
}

mode1.bin <- projecting_tm(mode2, method = 'binary') %>% sna.format
mode1.sum <- projecting_tm(mode2, method = 'sum') %>% sna.format
mode1.new <- projecting_tm(mode2, method = 'Newman') %>% sna.format
```

```{r fig.width=10, fig.height=10, echo = F}
#save the layout from the first plot to ensure that the other two line up
plot.coords <- gplot(mode1.bin, gmode = 'graph', displayisolates = T, edge.lwd = 1, edge.col=rgb(0, 0, 0, .25), displaylabels = T, label = row.names(dat),  label.cex = .7, main = 'Binary')

gplot(mode1.sum, gmode = 'graph', displayisolates = F,  edge.lwd = 1, edge.col=matrix(rgb(0, 0, 0, mode1.sum / max(mode1.sum)), nrow = dim(mode1.sum)[1]),displaylabels = T, label = row.names(dat),  label.cex = .7, coord = plot.coords, main = 'Sum')

gplot(mode1.new, gmode = 'graph', displayisolates = F, edge.lwd = 1, edge.col=matrix(rgb(0, 0, 0, mode1.new / max(mode1.new)), nrow = dim(mode1.new)[1]), displaylabels = T, label = row.names(dat),  label.cex = .7, coord = plot.coords, main = 'Newman')
```


##Node Centrality
###Degree
How do the different projection methods impact node-level statistics? Let's look by calculating the degree centrality of the raw two-mode networks and the three projected one-mode networks and comparing their distributions. [Click here for more information on how to think about centrality in two-mode networks](http://toreopsahl.com/tnet/two-mode-networks/node-centrality/).
```{r}
degrees <- cbind(degree(mode1.bin, gmode = 'graph'),
                degree(mode1.sum, gmode = 'graph'),
                degree(mode1.new, gmode = 'graph'), 
                degree_tm(mode2)[,2]) %>% melt
```

```{r fig.width = 10, fig.height=7, echo = F}
qplot(x = value,fill = factor(Var2), color = factor(Var2), data = degrees, geom = 'density', alpha = I(.5)) + 
     labs(title = 'Degree distributions under different projection methods', x = 'Degree centrality (# of nodes)', y = 'Density') + 
     scale_fill_discrete(name = 'Projection method', labels = c('Binary', 'Sum', 'Newman', 'None (raw two-mode)')) +
     scale_color_discrete(name = 'Projection method', labels = c('Binary', 'Sum', 'Newman', 'None (raw two-mode)')) +
     theme_minimal()
```

Describe results here . . .

###Geodesic Distance
Now let's look at the distribution of shortest path lengths across the weighted one-mode networks derived from each projection method. [Click here for more information](http://toreopsahl.com/tnet/two-mode-networks/shortest-paths/).

```{r}
distances <- cbind(distance_tm(mode2, projection.method = 'binary') %>% lower.tri.remove %>% c,
                  distance_tm(mode2, projection.method = 'sum') %>% lower.tri.remove %>% c,
                  distance_tm(mode2, projection.method = 'Newman') %>% lower.tri.remove %>% c) %>% melt
```

```{r fig.width = 10, fig.height=7, echo = F, warning = F}
qplot(x = value, fill = factor(Var2), color = factor(Var2), data = distances, geom = 'density', alpha = I(.5)) + 
     labs(title = 'Geodesic distributions under different projection methods', x = 'Geodesic distance (# of nodes)', y = 'Density') + 
     scale_fill_discrete(name = 'Projection method', labels = c('Binary', 'Sum', 'Newman')) +
     scale_color_discrete(name = 'Projection method', labels = c('Binary', 'Sum', 'Newman')) +
     theme_minimal()
```
Describe results here . . .